Context-dependent consequences of including lagged effects in demographic models

### 2022-05-24 docs/paper.Rmd
run everything

| Description                                  | Deterministic    | Stochastic, kernel-resampled | Stochastic, parameter-resampled (DLNM) |
|----------------------|----------------|----------------|-------------------|
| Mature plant survival                        | $s(z)$           | $s_y(z)$                     | $s(z;\theta_{0-36})$                   |
| Seedling survival                            | $s_0$            | $s_{0_y}$                    | $s_0(\theta_{0-36})$                   |
| Mature plant growth or regression            | $G(z^\prime, z)$ | $G_y(z^\prime,z)$            | $G(z^\prime,z;\theta_{0-36})$          |
| Seedling growth into mature plant            | $G_0(z^\prime)$  | $G_{0_y}(z^\prime)$          | $G(z^\prime;\theta_{0-36})$            |
| Probability of flowering                     | $p_f(z)$         | $p_{f_y}(z)$                 | $p_f(z;\theta_{0-36})$                 |
| Size-specific fecundity                      | $f(z)$           | $f(z)$                       | $f(z)$                                 |
| Probability of germination and establishment | $g$              | $g$                          | $g$                                    |

>>>>

| Description                                  | Deterministic    | Stochastic, kernel-resampled | Stochastic, parameter-resampled (DLNM) |
|----------------------------------------------|------------------|------------------------------|----------------------------------------|
| Mature plant survival                        | $s(z)$           | $s_y(z)$                     | $s(z;\theta_{0-36})$                   |
| Seedling survival                            | $s_0$            | $s_{0_y}$                    | $s_0(\theta_{0-36})$                   |
| Mature plant growth or regression            | $G(z^\prime, z)$ | $G_y(z^\prime,z)$            | $G(z^\prime,z;\theta_{0-36})$          |
| Seedling growth into mature plant            | $G_0(z^\prime)$  | $G_{0_y}(z^\prime)$          | $G(z^\prime;\theta_{0-36})$            |
| Probability of flowering                     | $p_f(z)$         | $p_{f_y}(z)$                 | $p_f(z;\theta_{0-36})$                 |
| Size-specific fecundity                      | $f(z)$           | $f(z)$                       | $f(z)$                                 |
| Probability of germination and establishment | $g$              | $g$                          | $g$                                    |
